Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-08-12 paper/lostanlenRelevanceScattering.tex
Add sensitivity analysis figure and subsection

The scaling parameter $q$ of the RBF kernels (see Eq.~\ref{eq:kc}) is set to $10\%$ of the number of data points to cluster.  As the number of Gaussians for the BoF approach, the numbers of clusters $M$ controls the level of abstraction. For each method, the parameter $M$ is set to $8$. It thus allows $8$ different types of observations to de modeled, which seems reasonable given the duration of the scene (30 seconds).

@@

>>>>

The scaling parameter $q$ of the RBF kernels (see Eq.~\ref{eq:kc}) is set to $10\%$ of the number of data points to cluster.  As the number of Gaussians for the BoF approach, the numbers of clusters $M$ controls the level of abstraction. For each method, the parameter $M$ is set to $8$. It thus allows $8$ different types of observations to de modeled, which seems reasonable given the duration of the scene (30 seconds). Note that this is the only free parameter in the proposed method. However, except for $\emph{RbQ-a}$, the results are not very sensitive to the choice of $M$, as long as it is large enough to characterize the seen. For a numerical demonstration of this, please see the end of the next section.

@@

\subsubsection*{Sensitivity to number of clusters $M$}

We now study the sensitivity of the precision at rank $5$ ($p@5$) with respect to the number of clusters $M$.
The results are shown in Figure \ref{fig:sensitivityM}.

For a small number of clusters ($M = 1$ or $M = 2$), all methods perform worse, since not enough discriminative sound objects are extracted from the recording.
This corresponds a summary statistics model.
For $M = 4$, most methods perform well, since this allows for better characterization of various signal structures in the scenes.
As the number of clusters increases, the \emph{RbQ-a} method performs significantly worse for both scattering features and MFCCs since any distinct objects are averaged out by clusters representing the background.
The \emph{RbQ-w} and \emph{RbQ-c} methods do better in this regard, as they are better able to emphasize the clusters that discriminate well between scenes.

Using \emph{RbQ-c}, therefore, we are not very sensitive to the choice of $M$, as long as it is large enough to allow for separation of the discriminative sound objects from the background.
This motivates our choice of $M = 8$ for the previous experiments in this section.

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{figures/sensitivityM}
\caption{Acoustic scene similarity retrieval in the DCASE 2013 private dataset: precision at rank $5$ ($p@5$) obtained for different methods as a function of the number of clusters $M$.}
\label{fig:sensitivityM}
\end{center}
\end{figure}
